---
title: "Assignment 2"
author: "Emily Berlinghoff"
date: "`r Sys.Date()`"
output:
    pdf_document: default
---

# Importing the data
```{r Importing Data, echo=FALSE}
# I've used R and Python for quantum computing before so I'm gonna use things we didn't learn in class for my own practice.
a2 <-  read.csv("assign.csv")
library(ggplot2)
install.packages("rmarkdown")
library(rmarkdown)
rmarkdown::render("Assignment2.Rmd",output_file="Assignment2.pdf")
```

# Question 1  

## Part a  
The explanatory variables based on the research quesiton are the **sex** and **screen**. We observe both of these variables to see how they affect the response variable of **physical**. 

## Part b  
The variable in the dataset I will use to answer the research question are **sex**, **screen**, and **tilt**. 

## Part c  
The categorical variable is **sex**. The qualitative variables are **screen** and **tilt**.

## Part d  
(remove this if you aren't doing any manipulation/transformation,etc.)


```{r}
# code for any manipulation/transformation - can remove if none!
```

# Question 2  


```{r Graph, echo=FALSE}
ggplot(a2, aes(x=screen, y=tilt colour=sex)) + # making x and y axis
    geom_point(size=3, shape=19, alpha=0.7) + # making the points
    geom_smooth(method="lm", se=FALSE) + # add linear trend lines without the confidence interval
    labs(title="Relationship Between Screen Time and Flexibility by Sex", # add title
        x="Screen Time (hours/day)",
        y="Tilt (degrees)",
        color="Sex") +
    theme_minimal() + # making it look nicer
    scale_colour_manual(values=c("blue","pink")) # blue for male and pink for male

```
